Structured Versus Decorated Cospans

### 2020-12-16 cospans.tex
tiny but important leftover

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we now show that this double isomorphism is a symmetric monoidal one, namely that $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0= \id_\A$ is a symmetric monoidal functor trivially. For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
\begin{align*}
\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')\in F(m+m')
%\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m')
\\
\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big) \\
&=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }F(\iota_m)x+F(\iota_{m'})x'\in F(m+m')
\end{align*}
The cospan part is equal, whereas we have an isomorphism between the decorations $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag} as follows
\begin{displaymath}
\begin{tikzcd}
F(m)\times F(m')\ar[rr,"\phi_{m,m'}"]\ar[d,"F(i_m)\times F(i_{m'})"']\ar[dr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] && F(m+m')\ar[d,equal]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(i_m+i_{m'})"description] \\
F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"']\ar[rr,dashed,bend right=15] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
 \end{tikzcd}
\end{displaymath}
We thus constructed isomorphisms $\lE(M)\otimes\lE(M')\cong\lE(M\otimes M')$ for any $M,M'$.
Notice that both sides in the diagram above, combined with the same object $(m+m')$ in $\A$, express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}. Therefore the pasted isomorphism is the canonical unique one that commutes with the respective cocones. This is useful when checking associativity for example: there is only one such isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans.

>>>>

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we now show that this double isomorphism is a symmetric monoidal one, namely that $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0= \id_\A$ is a symmetric monoidal functor trivially. For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
\begin{align*}
\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')\in F(m+m')
%\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m')
\\
\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big) \\
&=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }F(\iota_m)x+F(\iota_{m'})x'\in F(m+m')
\end{align*}
The cospan part is equal, whereas we have an isomorphism between the decorations $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag} as follows
\begin{displaymath}
\begin{tikzcd}
F(m)\times F(m')\ar[rr,"\phi_{m,m'}"]\ar[d,"F(i_m)\times F(i_{m'})"']\ar[dr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] && F(m+m')\ar[d,equal]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(i_m+i_{m'})"description] \\
F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"']\ar[rr,dashed,bend right=15] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
 \end{tikzcd}
\end{displaymath}
We thus constructed isomorphisms $\lE(M)\otimes\lE(M')\cong\lE(M\otimes M')$ for any $M,M'$.
Notice that both sides in the diagram above, combined with the same object $m+m'$ in $\A$, express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}. Therefore the pasted isomorphism is the canonical unique one that commutes with the respective cocones. This is useful when checking associativity for example: there is only one such isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans.
